---
title: "Rural, Urban, Coastal, Inland and Integrated Neighbourhood Working"
author: "Richard Blackwell"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    logo: logo.png
---

<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<script>
  $(document).ready(function() {
    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

    $('footnote').each(function(index) {
      var text  = $(this).html();
      var fnNum = (index+1).toString().sup();
      $(this).html(text + fnNum);

      var footnote   = fnNum + ' ' + $(this).attr('content') + '<br/>';
      var oldContent = $(this).parents('slide').children('div.footnotes').html();
      var newContent = oldContent + footnote;
      $(this).parents('slide').children('div.footnotes').html(newContent);
    });
  });
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(leaflet)
library(sf)
library(htmlwidgets)
library(conflicted)

# Load the RUCI classification
df_ruci <- read.csv('C:/Users/richard.blackwell/OneDrive - Health Innovation South West/Workspace/RUCI_analysis/ruci.csv')

# Load OA21 shapefile ----
sf_oa21 <- st_read(dsn = 'C:/Users/richard.blackwell/OneDrive - Health Innovation South West/Data/OpenGeography/Shapefiles/OA21',
                   layer = 'OA21') %>%
  st_transform(crs = 4326) %>%
  st_make_valid()

# Load BUA22 shapefile ----
sf_bua22 <- st_read(dsn = 'C:/Users/richard.blackwell/OneDrive - Health Innovation South West/Workspace/RUCI_analysis/data/BUA22',
                    layer = 'BUA22') %>%
  st_transform(crs = 4326) %>%
  st_make_valid()

# Load ICB23 shapefile ----
sf_icb23 <- st_read(dsn = 'C:/Users/richard.blackwell/OneDrive - Health Innovation South West/Workspace/RUCI_analysis/data/ICB23',
                    layer = 'ICB23') %>%
  st_transform(crs = 4326) %>%
  st_make_valid()

# Load Census 2021 resident population
df_popn_oa <- read.csv('C:/Users/richard.blackwell/OneDrive - Health Innovation South West/Workspace/RUCI_analysis/data/TS001/census2021-ts001-oa.csv') %>%
  select(3,4) %>%
  rename_with(.fn = ~c('OA21CD','POPN'))

# Join OA to RUCI
df_ruci <- df_ruci %>% 
  left_join(df_popn_oa, by = 'OA21CD')

# BUA22 RUCI
df_ruci_bua <- df_ruci %>% 
              mutate(RUCI = paste0(RUC, ' - ', CIC)) %>%
              dplyr::filter(grepl('^E', BUA22CD)) %>%
              group_by(BUA22CD, BUA22NM, BUA_CLASS, RUCI) %>% 
              summarise(BUA_POPN = mean(BUA_POPN, na.rm = FALSE),
                        POPN = sum(POPN, na.rm = FALSE),
                        .groups = 'keep') %>%
              ungroup()
hisw_lad <- c('Cornwall', 'Isles of Scilly', 
              'East Devon', 'Mid Devon', 'North Devon', 'West Devon',
              'Exeter', 'Plymouth', 'Torbay',
              'Torridge', 'Teignbridge', 'South Hams',
              'Somerset West and Taunton', 'South Somerset', 'Sedgemoor', 'Mendip')

hisw_bua <- df_ruci %>% dplyr::filter(LAD22NM %in% hisw_lad) %>% distinct(BUA22CD) %>% dplyr::filter(grepl('^E', BUA22CD)) %>% .$BUA22CD

hisw_oa <- df_ruci %>% dplyr::filter(LAD22NM %in% hisw_lad) %>% distinct(OA21CD) %>% .$OA21CD

# OA22 RUCI
df_ruci_oa <- df_ruci %>% 
              mutate(RUCI = paste0(RUC, ' - ', CIC)) %>%
              dplyr::filter(grepl('^E', BUA22CD)) %>%
              group_by(OA21CD, RUCI) %>% 
              summarise(POPN = sum(POPN, na.rm = FALSE),
                        .groups = 'keep') %>%
              ungroup()

# Add the RUCI classification and population to the BUA shapefile
sf_bua22_hisw <- sf_bua22 %>% dplyr::filter(BUA22CD %in% hisw_bua) %>%
  left_join(df_ruci_bua %>% select(-BUA22NM), by = 'BUA22CD')

# Add the RUCI classification and population to the OA shapefile
sf_oa21_hisw <- sf_oa21 %>% dplyr::filter(OA21CD %in% hisw_oa) %>%
  left_join(df_ruci %>% mutate(RUCI = paste0(RUC, ' - ', CIC)), by = 'OA21CD')


```


## Definitions

## Try out some footnotes

Lets assume I have a footnote <footnote content="The first awesome footnote!">here</footnote>. And here we are going to have another one: <footnote content="This is my second footnote!">#secFN</footnote>

### Map

```{r map, echo = TRUE}
palRUCI <- colorFactor(palette = c('Rural - Inland' = '#52731C', 'Rural - Coastal' = '#0084CC',
                                   'Urban - Inland' = '#B99B84', 'Urban - Coastal' = '#9BBDDB'),
                       na.color = '#ffffff',
                       levels = c('Rural - Inland', 'Rural - Coastal', 'Urban - Inland', 'Urban - Coastal'))

map <- leaflet() %>%
  addTiles(options = tileOptions(opacity = 0.3)) %>%
  addPolygons(data = sf_bua22_hisw %>% dplyr::filter(RUCI == 'Rural - Inland'),
              weight = 1,
              color = ~palRUCI(RUCI),
              opacity = 1,
              fillColor = ~palRUCI(RUCI),
              fillOpacity = 0.7,
              popup = ~sprintf('[%s] - %s<br>BUA Class: %s<br>RUCI Class: %s<br>Popn: %d', BUA22CD, BUA22NM, BUA_CLASS, RUCI, POPN),
              group = '[BUA] Rural - Inland') %>%
  addPolygons(data = sf_bua22_hisw %>% dplyr::filter(RUCI == 'Rural - Coastal'),
              weight = 1,
              color = ~palRUCI(RUCI),
              opacity = 1,
              fillColor = ~palRUCI(RUCI),
              fillOpacity = 0.7,
              popup = ~sprintf('[%s] - %s<br>BUA Class: %s<br>RUCI Class: %s<br>Popn: %d', BUA22CD, BUA22NM, BUA_CLASS, RUCI, POPN),
              group = '[BUA] Rural - Coastal') %>%  
    addPolygons(data = sf_bua22_hisw %>% dplyr::filter(RUCI == 'Urban - Inland'),
              weight = 1,
              color = ~palRUCI(RUCI),
              opacity = 1,
              fillColor = ~palRUCI(RUCI),
              fillOpacity = 0.7,
              popup = ~sprintf('[%s] - %s<br>BUA Class: %s<br>RUCI Class: %s<br>Popn: %d', BUA22CD, BUA22NM, BUA_CLASS, RUCI, POPN),
              group = '[BUA] Urban - Inland') %>%
  addPolygons(data = sf_bua22_hisw %>% dplyr::filter(RUCI == 'Urban - Coastal'),
              weight = 1,
              color = ~palRUCI(RUCI),
              opacity = 1,
              fillColor = ~palRUCI(RUCI),
              fillOpacity = 0.7,
              popup = ~sprintf('[%s] - %s<br>BUA Class: %s<br>RUCI Class: %s<br>Popn: %d', BUA22CD, BUA22NM, BUA_CLASS, RUCI, POPN),
              group = '[BUA] Urban - Coastal') %>%  
    addPolygons(data = sf_oa21_hisw %>% dplyr::filter(RUCI == 'Rural - Inland'),
                #stroke = FALSE,
                weight = 1,
                color = ~palRUCI(RUCI),
                opacity = 0.3,
                fillColor = ~palRUCI(RUCI),
                fillOpacity = 0.7,
                popup = ~sprintf('[%s]<br>[%s] - %s<br>RUCI Class: %s<br>Popn: %d', OA21CD, LAD22CD, LAD22NM, RUCI, POPN),
                group = '[OA] Rural - Inland') %>%
    addPolygons(data = sf_oa21_hisw %>% dplyr::filter(RUCI == 'Rural - Coastal'),
                #stroke = FALSE,
                weight = 1,
                color = ~palRUCI(RUCI),
                opacity = 0.3,
                fillColor = ~palRUCI(RUCI),
                fillOpacity = 0.7,
                popup = ~sprintf('[%s]<br>[%s] - %s<br>RUCI Class: %s<br>Popn: %d', OA21CD, LAD22CD, LAD22NM, RUCI, POPN),
                group = '[OA] Rural - Coastal') %>%
    addPolygons(data = sf_oa21_hisw %>% dplyr::filter(RUCI == 'Urban - Inland'),
                #stroke = FALSE,
                weight = 1,
                color = ~palRUCI(RUCI),
                opacity = 0.3,
                fillColor = ~palRUCI(RUCI),
                fillOpacity = 0.7,
                popup = ~sprintf('[%s]<br>[%s] - %s<br>RUCI Class: %s<br>Popn: %d', OA21CD, LAD22CD, LAD22NM, RUCI, POPN),
                group = '[OA] Urban - Inland') %>%
    addPolygons(data = sf_oa21_hisw %>% dplyr::filter(RUCI == 'Urban - Coastal'),
                #stroke = FALSE,
                weight = 1,
                color = ~palRUCI(RUCI),
                opacity = 0.3,
                fillColor = ~palRUCI(RUCI),
                fillOpacity = 0.7,
                popup = ~sprintf('[%s]<br>[%s] - %s<br>RUCI Class: %s<br>Popn: %d', OA21CD, LAD22CD, LAD22NM, RUCI, POPN),
                group = '[OA] Urban - Coastal') %>%
  addLegend(position = 'topright', pal = palRUCI, 
            values = c('Rural - Inland', 'Rural - Coastal', 'Urban - Inland', 'Urban - Coastal')) %>%
  addLayersControl(overlayGroups = c('[BUA] Rural - Inland', '[BUA] Rural - Coastal', 
                                     '[BUA] Urban - Inland', '[BUA] Urban - Coastal', 
                                     '[OA] Rural - Inland', '[OA] Rural - Coastal', 
                                     '[OA] Urban - Inland', '[OA] Urban - Coastal'))
map
#saveWidget(map, 'map.html')

```
